### 2019-01-16 Sections/costs_and_attributes_in_quantum_networks.tex
Fixed error, compressed photos

From this, we can then define the \textit{classical information of the channel}\index{c_i_c}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their \comment{classical information of the channel} is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B).
\end{align}
% \comment{Previously this was `classical mutual information'. Is that right? Isn't this actually the `accessible information'?}

>>>>

From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their \comment{classical information of the channel} is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B).
\end{align}
% \comment{Previously this was `classical mutual information'. Is that right? Isn't this actually the `accessible information'?}
